How to write a PhD in Biological Sciences: a guide for the uninitiated

### 2021-04-19 2.12-taxonomy.Rmd
Add files via upload
# Plant taxonomy update on advice of Al Ellis

## Scientific names and taxonomic authorities {#taxonomy}

@@

### Scientific names

@@

#### Consider this example:

@@

### Different codes for the nomenclature of different taxa

@@

#### Peculiarities of plant taxonomy

Plant taxonomy is considered the taxonomic mother discipline as the work of Linneaus in 1753 was the first botanical work that consistently used Linneus' binomial (two names: Genus species) nomeclatural system [@linnaeus1753species] which pre-dated the more inclusive (and better known) landmark publication in 1758 [@linnaeus1758systema]. In addition to the Latin binomial name (Genus and species), plants (and some other taxa) often require further descriptors or **ranks** that denote subspecies, varieties, subvareties, etc. I have included a (non-exhaustive) list of these in Table \@ref(tab:plantrank), together with some examples.

Because Linneaus named so many plant species is his landmark publications, instead of writing out the full taxonomic authority after the species names, botanists abbreviate this to "L.". Like Linneaus, other prolific plant taxonomists can have their names abbreviated, but plant taxonomists became so numerous that there needed to be some standardisation of names and their abbreviations. A database of these **Standard Forms** can be found at [the International Plant Names Index database](https://www.kew.org/data/authors.html). Note that Standard Forms in plant taxonomy can include initials.

@@

Some plants exist in associations (such as lichens which are an association between an algae or cyanobacteria and one or more fungi. For these associations there is a specific code for their nomenclature: International Code of Phytosociological Nomenclature [@theurillat2021international].

@@

### Common names

@@

### Should common names have capitals?

@@

#### View 1.

@@

#### View 2.

>>>>

# Scientific names and taxonomic authorities {#taxonomy}

@@

## Scientific names

@@

### Consider this example:

@@

## Different codes for the nomenclature of different taxa

@@

### Peculiarities of plant taxonomy

Plant taxonomy is considered the taxonomic mother discipline as the work of Linneaus in 1753 was the first botanical work that consistently used Linneus' binomial (two names: Genus species) nomeclatural system [@linnaeus1753species] which pre-dated the more inclusive (and better known) landmark publication in 1758 [@linnaeus1758systema]. Until the Botanical Code was revised in 2012, all new botanical diagnoses had to be written in Latin. In addition to the Latin binomial name (Genus and species), plants (and some other taxa) often require further descriptors or **ranks** that denote subspecies, varieties, subvareties, etc. I have included a (non-exhaustive) list of these in Table \@ref(tab:plantrank), together with some examples.

Unlike animal authorities, for plants if the combination of Genus and species has changed, both the authority for the original genus placement, and the author responsible for the new combination are given after the species name (with the former in brackets). In addition, for plants no year is given, and the name of the authority is usually abbreviated. Because Linneaus named so many plant species is his landmark publications, instead of writing out the full taxonomic authority after the species names, botanists abbreviate this to "L.". Like Linneaus, other prolific plant taxonomists can have their names abbreviated, but plant taxonomists became so numerous that there needed to be some standardisation of names and their abbreviations. A database of these **Standard Forms** can be found at [the International Plant Names Index database](https://www.kew.org/data/authors.html). Note that Standard Forms in plant taxonomy can include initials.

@@

Algae sometimes exist in association with other taxa (such as lichens which are an association between an algae or cyanobacteria and one or more fungi. For these associations there is a specific code for their nomenclature: International Code of Phytosociological Nomenclature [@theurillat2021international].

@@

## Common names

@@

## Should common names have capitals?

@@

### View 1.

@@

### View 2.
